Efficient Coalition Formation for Web Services

### 2013-03-07 papers/coalition/coalition.tex
CHanges
Changes

\begin{abstract}
Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different communities for better efficiency, market share and total payoff. There are number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention. In this paper, we analyze coalition formations using cooperative game-theoretic methods. We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities, Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and simulation results proves that our algorithms provide web services and community owners with applicable and near optimal decision making mechanisms.

@@

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions. 
This merge-and-split algorithm is designed to be adoptable for different problems. It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition. Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$). As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.

@@

\begin{equation*}
v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times C_{coef}} \times w_{metric} } \times ms_{ws}}
\end{equation*}

>>>>

\begin{abstract}

Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different groups called communities. Communities aim to provide better efficiency, market share and total payoff. There are a number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention. In this paper, we propose an efficient coalition formation mechanism using cooperative game-theoretic methods. We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities. Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and simulation results show that our algorithms provide web services and community owners with applicable and near-optimal decision making mechanisms.

@@

In coalition-formation games, formation of the coalitions is the most important aspect of in the game. These solutions focus on maximizing social welfare. For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare. The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$. There are $centralized$ algorithms for this end, however these approaches are generally NP-complete. The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions. 
%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity. However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}. 
In our application, we prefer not having a centralized decision maker dictating all web services their decisions. Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker. The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}. The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well. It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions. 
This merge-and-split algorithm is designed to be adoptable for different problems. It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition. Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$. For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services). In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff. ($p_i \geq q_i$ with at least one element $p_i > q_i$). As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function. More details of this algorithm and analyses of generic solutions on these types of games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

\begin{equation*}
v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times CC{m} \times ms_{ws}} \times w_{metric} } }
\end{equation*}
